---
title: "Project 3"
output: html_notebook
---

### Materia: Analítica y Visualización de Datos, 5CDM1

##### Alumnos:

##### De Luna Ocampo Yanina

##### Ramírez Méndez Kevin

##### Data: Iris

##### Select the libraries we are going to use
```{r}
library("ggplot2")
```

##### Importing data
```{r}
dat <- iris
```

##### See the first six rows of the data
```{r}
head(dat)
```

##### View all the data
```{r}
View(dat)
```

##### Separating the data
```{r}
df_Setosa = dat[dat$class == "Iris-setosa",]
df_Versicolor = dat[dat$class == "Iris-versicolor",]
df_Virginica = dat[dat$class == "Iris-virginica",]
```

##### Combine df_Setosa, df_Versicolor and df_Virginica and use sapply that interpret the output to the most fundamental data structure possible
```{r}
theList <- as.data.frame(t(c(df_Setosa[-1])), row.names = NULL)

dfThree_Iris <- rbind(df_Setosa, df_Versicolor, df_Virginica)
dat = dat[,-5]
dfThree_Iris <- sapply(dfThree_Iris, as.numeric)
```

##### Use the mahalanobis function to see the distance
```{r}
dfThree_Iris$mahalanobis <- mahalanobis(dat, colMeans(dat), cov(dat))
print(dfThree_Iris)
```

##### The visualization of what we are looking for
```{r}
num.outliers <- 3
mah.ordenacion <- order(mahalanobis(dat , colMeans(dat), cov(dat)), decreasing=TRUE)
ouLi_3 <- rep(FALSE , nrow(dat))
ouLi_3[mah.ordenacion[1:num.outliers]] <- TRUE
colorear.outlier <- ouLi_3 * 50

plot(dat , pch=0)
points(dat , pch=colorear.outlier)
```